\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-09-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added abstract

	\begin{abstract} TBC
		%  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints. We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically. New theorems establish that the true predictive distribution can be recovered in the elliptical case by linear reconciliation, and general conditions are derived for when this is a projection. A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense. Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints. Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
	\end{abstract}

>>>>

	\begin{abstract} 
		A geometric interpretation is developed for so-called {\em reconciliation} methodologies which are used to forecast time series that adhere to known linear constraints.  In particular, a general framework is established nesting many existing popular reconciliation methods within the class of {\em projections}.  This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecasts with respect to a specific class of loss functions.  This result is later demonstrated empirically.  The geometric interpretation is also used to provide a new proof that forecast reconciliation results in unbiased forecasts as long as the initial so-called {\em base} forecasts are also unbiased.  Approaches for dealing with biased base forecasts are proposed and explored in an extensive empirical study on Australian tourism demand.  Overall, the method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.

	\end{abstract}
